BayesPy: Variational Bayesian Inference in Python

### 2015-03-13 response.tex

\begin{document}

\maketitle

\section{Responses to the Reviewers of Submission 14-324 (v1)}

I want to express my gratitude to the action editor and all three reviewers for
their in-depth evaluation and constructive comments.  I have taken into account
the reviews and revised the paper.  In addition, I have added some new features
to BayesPy and released a new version (0.3.1).  The four major changes in this
revised submission can be listed as:
\begin{itemize}

\item BayesPy now supports several advanced VB techniques: stochastic
  variational inference, collapsed inference, Riemannian conjugate gradient
  learning, pattern searches and deterministic annealing.

\item The extremely simple example in the previous submission has been replaced
  by a Gaussian mixture model example.

\item A detailed comparison to Infer.NET has been added.

\item The reported installation issues have been fixed.

\end{itemize}
More detailed responses for each reviewer are given below.

@@

% \end{itemize}

\subsection{Reviewer 1}

\begin{itemize}

\item \underline{syntax}
  \\
  The API in the online documentation (bayespy.org) provides details about the
  syntax for nodes and methods.  For instance, more details about the syntax of
  the gating node has been added in the documentation.  However, it is typically
  better to use Mixture node directly to achieve mixture distributions, as shown
  in the example in section 3.

\item \underline{speed comparison}
  \\
  The revised version contains a more detailed comparison with Infer.NET.  The
  other relevant active packages are basically MCMC packages.  Because it is not
  obvious how to weigh different aspects of MCMC and VB methods in general, a
  comparison with the MCMC packages is out of the scope of this paper.  However,
  because Infer.NET seems to offer practically the same functionality, section 4
  provides a detailed comparison between BayesPy and Infer.NET, including a
  speed comparison.

\item \underline{supported models}
  \\
  The revised version makes it more clear that BayesPy supports conjugate
  exponential family models and does not currently support non-conjugate models.
  An example of a non-supported model is given in section 4.  Examples of
  supported popular models are listed in section 2.  Section 3 also provides an
  example implementation of a Gaussian mixture model, which is much more
  interesting model than the very simple model in the previous version of the
  paper.  Because of the page limit, more examples are provided in the online
  documentation.  Section 4 also discusses Gaussian mixture and PCA models,
  which are given implementations in the supplementary material.  The results in
  the section also provide some rough idea about computational costs and how
  large models can be constructed without using stochastic variational
  inference.

\item \underline{scheduling}
  \\
  The updates (and all computations) are performed sequentially, that is,
  variables are updated in turns.  This is now mentioned in Section 3.  Parallel
  computing is not supported.

@@

\end{itemize}

\subsection{Reviewer 2}

\begin{itemize}

\item \underline{installation}
  \\
  The installation instructions in the online documentation (bayespy.org) have
  been improved.  Because BayesPy itself is written purely in Python and thus
  does not need compiling, the only challenge is in installing the requirements
  (a recent NumPy stack).  In order to make the installation of the NumPy stack
  much easier, the instructions mention the possibility to use pre-built
  versions of the NumPy stack (e.g., Anaconda or Enthought).  This is quite
  close to having a stand-alone executable as suggested.

  The reviewer was not able to use the package because the execution halted.
  This was caused by an unfortunate regression bug in matplotlib 1.4.0 and a
  workaround for it in BayesPy.  These issues have now been fixed.  I want to
  thank the reviewer for reporting the bug.

  The error in the second installation seems to be caused by a server error in
  PyPI website (or altenatively some issue in matplotlib), according to my
  understanding.  I hope the reviewer does not experience this issue anymore.

\item \underline{section headings}
  \\
  Section 2 is now labelled ``Features''.

\item \underline{user community}
  \\
  It is difficult to give any accurate estimates of the size of the user
  community.  However, based on given stars, the number of forks and reported
  issues on Github, there seems to be interested users.  In addition, the number
  of downloads in pypi.org and mloss.org give some idea about the number of
  users.

\item \underline{speed comparison}
  \\
  The revised version contains a more detailed comparison with Infer.NET.  The
  other relevant active packages are basically MCMC packages.  It is not obvious
  how to weigh different aspects of MCMC and VB methods in general, thus a
  comparison to the MCMC packages is out of the scope of this paper.  However,
  because Infer.NET seems to offer practically the same functionality, section 4
  provides a detailed comparison between BayesPy and Infer.NET, including a
  speed comparison.

@@

\end{itemize}

\subsection{Reviewer 3}

Reviewer 3 did not point out any modifications the author should make.

### 2015-03-13 bayespy.tex
Almost ready revised version

\begin{keywords}
  Variational Bayes, variational message passing, Python, probabilistic
  programming
\end{keywords}

@@

BayesPy is a Python 3 package providing tools for constructing models and
performing VB inference easily and efficiently.  It is based on the variational
message passing (VMP) framework which defines a simple message passing protocol
\citep{Winn:2005}.  This enables implementation of small general nodes that can
be used as building blocks for large complex models.  BayesPy offers a
comprehensive collection of built-in nodes that can be used to build a wide
range of models and a simple interface for implementing custom nodes.  The
package is released under the GNU General Public License v3.0 (GPLv3).

@@

Nodes are the key part of BayesPy as they are used to construct the model.
There are two types of nodes in BayesPy: stochastic and deterministic.
Stochastic nodes correspond to probability distributions and deterministic nodes
correspond to functions.  Built-in stochastic nodes include all common
exponential family distributions (e.g., Gaussian, gamma and Dirichlet
distributions), a general mixture distribution and a few complex nodes for
dynamic variables (e.g., discrete and Gaussian Markov chains).  Built-in
deterministic nodes include a gating node and a general sum-product node.
%The
%documentation also provides instructions for implementing new nodes in case the
%built-in collection is insufficient.
In case a model cannot be constructed using the built-in nodes, the
documentation provides instructions for implementing new nodes.

BayesPy is designed to be simple enough for average users but flexible and
efficient enough for expert users.  One goal is to keep the syntax easy and
intuitive to read and write by making it similar to the mathematical formulation
of the model.  Missing values are easy to handle and the variables can be
monitored by plotting the posterior distributions during the learning.  BayesPy
has also preliminary support for some advanced VB methods such as stochastic
variational inference \citep{Hoffman:2013}, deterministic annealing
\citep{Katahira:2008}, collapsed inference \citep{Hensman:2012},
Riemannian-gradient-based optimization \citep{Honkela:2010}, parameter
expansions \citep{Qi:2007} and pattern searches \citep{Honkela:2003}.  For
developers, the unit testing framework helps in finding bugs, making changes and
implementing new features in a robust manner.

BayesPy can be installed similarly to other Python packages.  It requires Python
3 and a few popular packages: NumPy, SciPy, matplotlib and h5py.  The latest
release can be installed from Python Package Index (PyPI) and detailed
instructions can be found from the comprehensive online documentation
\citep{bayespy.org}.  The latest development version is available at
GitHub\footnote{\url{https://github.com/bayespy/bayespy}}, which is also the
platform used for reporting bugs and making pull requests.

@@

This section demonstrates BayesPy with a Gaussian mixture model.  A simple
artificial dataset is created by drawing 200 samples from a 2-dimensional
Gaussian distribution.  80 samples have mean $[1, 1]$ and 120 samples have mean
$[0, 0]$:
\begin{lstlisting}
import numpy as np
N = 200, D = 2
data = np.random.randn(N, D)
data[:80,:] += np.ones(D)
\end{lstlisting}
We construct a mixture model for the data and assume that the parameters, the
cluster assignments and the true number of clusters are unknown.  The model uses
a maximum number of five clusters but the effective number of clusters will be
determined automatically:
\begin{lstlisting}
K = 5
\end{lstlisting}
The unknown cluster means and precision matrices are given Gaussian and Wishart
prior distributions:
\begin{lstlisting}
from bayespy import nodes
mu = nodes.Gaussian(np.zeros(D), 0.01*np.identity(D), plates=(K,))
Lambda = nodes.Wishart(D, 0.01*np.identity(D), plates=(K,))
\end{lstlisting}
The \texttt{plates} keyword argument is used to define repetitions similarly as
the plate notation in graphical models.  The cluster assignments are categorical
variables, and the cluster probabilities are given a Dirichlet prior
distribution:
\begin{lstlisting}
alpha = nodes.Dirichlet(0.01*np.ones(K))
z = nodes.Categorical(alpha, plates=(N,))
\end{lstlisting}
The observations are from a Gaussian mixture distribution:
\begin{lstlisting}
y = nodes.Mixture(Z, nodes.Gaussian, mu, Lambda)
\end{lstlisting}
The second argument for the \texttt{Mixture} node defines the type of the
mixture distribution, in this case Gaussian.  The variable is marked as observed
by providing the data:
\begin{lstlisting}
y.observe(data)
\end{lstlisting}
Next, we want to find the posterior approximation for our latent variables.  We
create the variational Bayesian inference engine:
\begin{lstlisting}
from bayespy.inference import VB
Q = VB(y, mu, z, Lambda, alpha)
\end{lstlisting}
Before running the VMP algorithm, the symmetry in the model is broken by
a random initialization of the cluster assignments:
\begin{lstlisting}
z.initialize_from_random()
\end{lstlisting}
Without the random initialization, the clusters would not be separated.  The VMP
algorithm is run for 100 iterations or until convergence:
\begin{lstlisting}
Q.update(repeat=100)
\end{lstlisting}
The results can be examined, for instance, by printing the posterior
distributions of some variables:
\begin{lstlisting}
print(alpha)
print(mu)
\end{lstlisting}
In addition, module \texttt{bayespy.plot} contains several plotting functions to
examine the results visually.

@@

This section provides a brief comparison with Infer.NET because it is another
active project implementing the variational message passing algorithm, whereas
the other related active projects implement MCMC.  The main advantages of
Infer.NET over BayesPy are its support for non-conjugate models and other
inference engines.  On the other hand, BayesPy is open-source software and
supports several advanced VB methods (e.g., stochastic variational inference and
collapsed inference).

The speed of the packages were compared by using two widely used models: a
Gaussian mixture model (GMM) and principal component analysis
(PCA).\footnote{The scripts for running the experiments are available in the
  supplementary material.}  Both models were run for small and large
artificially generated datasets.  For GMM, the small model used 10 clusters for
200 observations with 2 dimensions, and the large model used 40 clusters for
2000 observations with 10 dimensions.  For PCA, the small model used
10-dimensional latent space for 500 observations with 20 dimensions, and the
large model used 40-dimensional latent space for 2000 observations with 100
dimensions.  Infer.NET used a fully factorizing approximation for the PCA model,
whereas BayesPy did not factorize with respect to the latent space dimensions.
The experiments were run on a Linux computer with a quad-core processor
(i7-4702MQ).  Because the packages run practically identical algorithms and thus
converged to similar solutions in a similar number of iterations (50--100
iterations depending on the dataset), we compare the average CPU time per
iteration.

The results are summarized in Table~\ref{tab:speed}.  On the smaller datasets,
Infer.NET is slightly faster because BayesPy has some overhead of Python.
However, on the larger datasets, BayesPy is significantly faster because it uses
BLAS and LAPACK libraries for fast numerical operations.\footnote{Assuming that
  NumPy uses BLAS/LAPACK because BayesPy uses NumPy for numerical operations.}
In addition, if using multi-threaded BLAS and LAPACK, the difference in
wall-clock time can be even larger than in CPU time.  The speed of BayesPy for
these models could potentially be improved by using collapsed or stochastic
variational inference, and the accuracy could be improved by using
Gaussian-Wishart nodes which do not factorize with respect to the Gaussian and
Wishart variables.

@@

% related active software projects discussed in the introduction,

% Because the other
% active Bayesian software packages discussed in the introduction do not implement
% the variational message passing algorithm,

%* compiled

%* non-conjugate

%* other engines

%* open source

%* advanced

%* dynamic nodes

% \begin{figure}
%   \centering
%   \begin{tikzpicture}
%     \node [obs] (yn) {$y_n$};
%     \node [latent, above left=of yn] (mu) {$\mu$};
%     \node [latent, above right=of yn] (tau) {$\tau$};

%     \edge {mu, tau} {yn};

%     \tikzstyle{plate caption} = [caption, node distance=0, inner sep=0pt,
%     below=5pt of #1.south]

%     \plate {} {(yn)} {$n=1,\ldots,10$};
%   \end{tikzpicture}
%   \caption{Graphical model of the example problem.}
%   \label{fig:graphical_model}
% \end{figure}
% In order to demonstrate BayesPy, this section solves an extremely simple problem
% but which includes the main steps of using BayesPy.  The task is to estimate the
% unknown mean and precision parameters of a Gaussian distribution given ten
% observations.  Thus, the likelihood function is Gaussian:
% \begin{align*}
%   p(y_1,\ldots,y_{10}|\mu,\tau) &= \prod^{10}_{n=1}\mathcal{N}(y_n | \mu, \tau),
% \end{align*}
% where the Gaussian distribution is parameterized by precision instead of
% variance.  The unknown mean $\mu$ and precision $\tau$ are given broad Gaussian
% and gamma priors, respectively:
% \begin{align*}
%   p(\mu) &= \mathcal{N}(\mu|0, 10^{-6}), & p(\tau) &= \mathcal{G}(\tau|10^{-6},
%   10^{-6}).
% \end{align*}
% Figure~\ref{fig:graphical_model} shows the graphical model of this simple model.
% The model is constructed in BayesPy by creating nodes:
% \begin{lstlisting}
% from bayespy.nodes import GaussianARD, Gamma
% mu = GaussianARD(0, 1e-6)
% tau = Gamma(1e-6, 1e-6)
% \end{lstlisting}
% These two nodes represent the two unknown variables that we are interested in.
% They are the parameters of the Gaussian distribution of the observed variable:
% \begin{lstlisting}
% y = GaussianARD(mu, tau, plates=(10,))
% \end{lstlisting}
% The number of observations is given as plates which define the number of
% repetitions.  Note that the syntax of the model construction is similar to the
% mathematical formulation which defines the conditional distributions for each
% variable.  Thus, it is easy to understand the model from the Python code.  After
% the model has been constructed, some nodes are marked as observed and given
% data:
% \begin{lstlisting}
% y.observe([4.5, 3.9, 6.3, 5.6, 4.9, 2.8, 7.4, 6.1, 4.8, 2.1])
% \end{lstlisting}
% Next, we want to find the posterior approximation for our latent variables.  We
% create the VB inference engine:
% \begin{lstlisting}
% from bayespy.inference import VB
% Q = VB(y, mu, tau)
% \end{lstlisting}
% The inference engine takes all the stochastic nodes of the model as input.  The
% message passing algorithm can be run by calling \texttt{update} method:
% \begin{lstlisting}
% Q.update(repeat=100)
% \end{lstlisting}
% The algorithm is run for 100 iterations or until it converges.  In this case,
% the algorithm converges in four iterations.  The posterior approximation can be
% examined, for instance, by plotting the probability density functions of the
% latent variables:
% \begin{lstlisting}
% import bayespy.plot as bpplt
% import numpy as np
% bpplt.pyplot.figure()
% bpplt.pdf(Q[mu], np.linspace(0, 10, num=300))
% bpplt.pyplot.figure()
% bpplt.pdf(Q[tau], np.linspace(0, 2, num=300))
% bpplt.pyplot.show()
% \end{lstlisting}
% Figure~\ref{fig:posterior} shows the resulting approximate posterior
% distributions.  The module \texttt{bayespy.plot} contains functions for simple
% plotting tasks, such as plotting the probability density function or the Hinton
% diagram of a variable.  Note that the standard \texttt{pyplot} module of
% Matplotlib is available at the \texttt{plot} module of BayesPy.
% \begin{figure}
%   \begin{center}
%     \begin{subfigure}[b]{0.4\textwidth}
%       \includegraphics[width=\textwidth]{fig_mu}
%       \caption{$q(\mu)$}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.4\textwidth}
%       \includegraphics[width=\textwidth]{fig_tau}
%       \caption{$q(\tau)$}
%     \end{subfigure}
%   \end{center}
%   \caption{The posterior approximations of $\mu$ and $\tau$.}
%   \label{fig:posterior}
% \end{figure}

@@

BayesPy provides a simple and efficient way to construct conjugate exponential
family models and to find the variational Bayesian posterior approximation in
Python.
%
In addition to the standard variational message passing, it supports several
advanced methods such as stochastic and collapsed variational inference.  Future
plans include support for non-conjugate models and non-parametric nodes (e.g.,
Gaussian and Dirichlet processes).
% Future plans for BayesPy include implementing more inference engines (e.g.,
% maximum likelihood, expectation propagation and Gibbs sampling), improving the
% VB engine (e.g., collapsed variational inference \citep{Hensman:2012} and
% Riemannian conjugate gradient method \citep{Honkela:2010}) and implementing nodes
% for non-parametric models (e.g., Gaussian processes and Dirichlet processes).

@@

\vskip 0.2in
\bibliography{bibliography/bibliography.bib}

>>>>

\begin{keywords}
  Variational Bayes, probabilistic programming,
  %variational message passing,
  Python
\end{keywords}

@@

BayesPy is a Python 3 package providing tools for constructing conjugate
exponential family models and performing VB inference easily and efficiently.
It is based on the variational message passing (VMP) framework which defines a
simple message passing protocol \citep{Winn:2005}.  This enables implementation
of small general nodes that can be used as building blocks for large complex
models.  BayesPy offers a comprehensive collection of built-in nodes that can be
used to build a wide range of models and a simple interface for implementing
custom nodes.  The package is released under the GNU General Public License v3.0
(GPLv3).

@@

Nodes are the key part of BayesPy as they are used to construct the model.
BayesPy has two types of nodes: stochastic and deterministic.  Stochastic nodes
correspond to probability distributions and deterministic nodes correspond to
functions.  Built-in stochastic nodes include all common exponential family
distributions (e.g., Gaussian, gamma and Dirichlet distributions), a general
mixture distribution and a few complex nodes for dynamic variables (e.g.,
discrete and Gaussian Markov chains).  Built-in deterministic nodes include a
gating node and a general sum-product node.
%The
%documentation also provides instructions for implementing new nodes in case the
%built-in collection is insufficient.
In case a model cannot be constructed using the built-in nodes, the
documentation provides instructions for implementing new nodes.

BayesPy is designed to be simple enough for average users but flexible and
efficient enough for expert users.  One goal is to keep the syntax easy and
intuitive to read and write by making it similar to the mathematical formulation
of the model.  Missing values are easy to handle and the variables can be
monitored by plotting the posterior distributions during the learning.  BayesPy
has also preliminary support for some advanced VB methods such as stochastic
variational inference \citep{Hoffman:2013}, deterministic annealing
\citep{Katahira:2008}, collapsed inference \citep{Hensman:2012},
Riemannian conjugate gradient learning \citep{Honkela:2010}, parameter
expansions \citep{Qi:2007} and pattern searches \citep{Honkela:2003}.  For
developers, the unit testing framework helps in finding bugs, making changes and
implementing new features in a robust manner.

BayesPy can be installed similarly to other Python packages.  It requires Python
3 and a few popular packages: NumPy, SciPy, matplotlib and h5py.  The latest
release can be installed from Python Package Index (PyPI) and detailed
instructions can be found from the comprehensive online
documentation\footnote{\url{http://bayespy.org}}.  The latest development
version is available at
GitHub\footnote{\url{https://github.com/bayespy/bayespy}}, which is also the
platform used for reporting bugs and making pull requests.

@@

This section demonstrates the key steps in using BayesPy.  An artificial
Gaussian mixture dataset is created by drawing 500 samples from two
2-dimensional Gaussian distributions.  200 samples have mean $[2, 2]$ and 300
samples have mean $[0, 0]$:
\begin{lstlisting}
import numpy as np
N = 500; D = 2
data = np.random.randn(N, D)
data[:200,:] += 2*np.ones(D)
\end{lstlisting}
We construct a mixture model for the data and assume that the parameters, the
cluster assignments and the true number of clusters are unknown.  The model uses
a maximum number of five clusters but the effective number of clusters will be
determined automatically:
\begin{lstlisting}
K = 5
\end{lstlisting}
The unknown cluster means and precision matrices are given Gaussian and Wishart
prior distributions:
\begin{lstlisting}
from bayespy import nodes
mu = nodes.Gaussian(np.zeros(D), 0.01*np.identity(D), plates=(K,))
Lambda = nodes.Wishart(D, D*np.identity(D), plates=(K,))
\end{lstlisting}
The \texttt{plates} keyword argument is used to define repetitions similarly as
the plate notation in graphical models.  The cluster assignments are categorical
variables, and the cluster probabilities are given a Dirichlet prior
distribution:
\begin{lstlisting}
alpha = nodes.Dirichlet(0.01*np.ones(K))
z = nodes.Categorical(alpha, plates=(N,))
\end{lstlisting}
The observations are from a Gaussian mixture distribution:
\begin{lstlisting}
y = nodes.Mixture(z, nodes.Gaussian, mu, Lambda)
\end{lstlisting}
The second argument for the \texttt{Mixture} node defines the type of the
mixture distribution, in this case Gaussian.  The variable is marked as observed
by providing the data:
\begin{lstlisting}
y.observe(data)
\end{lstlisting}
Next, we want to find the posterior approximation for our latent variables.  We
create the variational Bayesian inference engine:
\begin{lstlisting}
from bayespy.inference import VB
Q = VB(y, mu, z, Lambda, alpha)
\end{lstlisting}
Before running the VMP algorithm, the symmetry in the model is broken by
a random initialization of the cluster assignments:
\begin{lstlisting}
z.initialize_from_random()
\end{lstlisting}
Without the random initialization, the clusters would not be separated.  The VMP
algorithm updates the variables in turns and is run for 200 iterations or until
convergence:
\begin{lstlisting}
Q.update(repeat=200)
\end{lstlisting}
The results can be examined visually by using \texttt{bayespy.plot} module:
\begin{lstlisting}
import bayespy.plot as bpplt
bpplt.gaussian_mixture_2d(y, alpha=alpha)
bpplt.pyplot.show()
\end{lstlisting}
It is also possible to print the parameters of the approximate posterior
distributions:
\begin{lstlisting}
print(alpha)
\end{lstlisting}
The \texttt{bayespy.plot} module contains also other functions for visually
examining the distributions.
%In addition, module \texttt{bayespy.plot} contains several plotting functions to
%examine the results visually.

@@

This section provides a brief comparison with Infer.NET because it is another
active project implementing the variational message passing algorithm, whereas
the other related active projects implement MCMC.  The main advantages of
Infer.NET over BayesPy are its support for non-conjugate models (e.g., logistic
regression) and other inference engines.  On the other hand, BayesPy is
open-source software and supports several advanced VB methods (e.g., stochastic
variational inference and collapsed inference).

The speed of the packages were compared by using two widely used models: a
Gaussian mixture model (GMM) and principal component analysis
(PCA).\footnote{The scripts for running the experiments are available as
  supplementary material.}  Both models were run for small and large
artificially generated datasets.  For GMM, the small model used 10 clusters for
200 observations with 2 dimensions, and the large model used 40 clusters for
2000 observations with 10 dimensions.  For PCA, the small model used
10-dimensional latent space for 500 observations with 20 dimensions, and the
large model used 40-dimensional latent space for 2000 observations with 100
dimensions.  Infer.NET used a fully factorizing approximation for the PCA model,
whereas BayesPy did not factorize with respect to the latent space dimensions.
The experiments were run on a Linux computer with a quad-core processor
(i7-4702MQ).  Because the packages run practically identical algorithms and thus
converged to similar solutions in a similar number of iterations (50--100
iterations depending on the dataset), we compare the average CPU time per
iteration.

The results are summarized in Table~\ref{tab:speed}.  On the smaller datasets,
Infer.NET is slightly faster because BayesPy has some Python overhead.  However,
the total CPU time for both methods is only a few seconds.  On the larger
datasets, BayesPy is significantly faster because it uses BLAS and LAPACK
libraries for fast numerical operations.\footnote{Assuming that NumPy uses
  BLAS/LAPACK because BayesPy uses NumPy for numerical operations.}  In
addition, if using multi-threaded BLAS and LAPACK on a multi-core computer, the
difference in wall-clock time can be even larger than in CPU time.  The speed of
BayesPy for these models could potentially be improved by using collapsed or
stochastic variational inference.  The accuracy could be improved by using
Gaussian-Wishart nodes which do not factorize with respect to the Gaussian and
Wishart variables.

@@

@@

BayesPy provides a simple and efficient way to construct conjugate exponential
family models and to find the variational Bayesian posterior approximation in
Python.
%
In addition to the standard variational message passing, it supports several
advanced methods such as stochastic and collapsed variational inference.  Future
plans include support for non-conjugate models and non-parametric models (e.g.,
Gaussian and Dirichlet processes).
% Future plans for BayesPy include implementing more inference engines (e.g.,
% maximum likelihood, expectation propagation and Gibbs sampling), improving the
% VB engine (e.g., collapsed variational inference \citep{Hensman:2012} and
% Riemannian conjugate gradient method \citep{Honkela:2010}) and implementing nodes
% for non-parametric models (e.g., Gaussian processes and Dirichlet processes).

@@

\vskip 0.2in
\small
\bibliography{bibliography/bibliography.bib}
